The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-11-12 paper/ms.tex
keith affiliation and wording

% This author list is not final! If you think you should be in a different position please do not hesitate to say so.
\author[B. J. S. Pope et al.]{Benjamin J. S. Pope,$^{1,2,3}$\thanks{E-mail: benjamin.pope@nyu.edu}
Guy R. Davies,$^{4,5}$
Keith Hawkins,$^{6,7}$
Timothy R. White,$^{5,8}$\newauthor
Timothy R. Bedding,$^{9,5}$
Allyson Bieryla,$^{10}$
David W. Latham,$^{10}$,
Conny Aerts,$^{11,12,13}$\newauthor
Suzanne Aigrain,$^{3}$ 
Victoria Antoci,$^{5}$
Dominic M. Bowman,$^{11}$
Ashley Chontos,$^{9}$\newauthor
Gilbert A. Esquerdo,$^{10}$
Daniel Huber,$^{14,15,9}$
Paula Jofr\'{e},$^{16}$
Simon Murphy,$^{5,9}$\newauthor
Timothy van Reeth,$^{5,9}$
Victor Silva Aguirre,$^{5}$
Amalie Stokholm,$^{5}$
Jie Yu,$^{9,5}$ \newauthor
and friends
\\
% List of institutions
$^{1}$Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA\\
$^{2}$NASA Sagan Fellow\\
$^{3}$Oxford Astrophysics, Denys Wilkinson Building, University of Oxford, OX1 3RH, Oxford, UK\\
$^{4}$School of Physics and Astronomy, University of Birmingham, Birmingham B15 2TT, UK\\
$^{5}$Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, Ny Munkegade 120, DK-8000 Aarhus C, Denmark\\
$^{6}$Department of Astronomy, The University of Texas at Austin, 2515 Speedway Boulevard, Austin, TX 78712, USA\\
$^{7}$Department of Astronomy, Columbia University, 550 W 120th St, New York, NY 10027, USA\\
$^{8}$Research School of Astronomy and Astrophysics, Mount Stromlo Observatory, The Australian National University, Canberra, ACT 2611, Australia\\
$^{9}$Sydney Institute for Astronomy (SIfA), School of Physics, University of Sydney, NSW 2006, Australia\\
$^{10}$Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA\\
$^{11}$Institute of Astronomy, KU Leuven, Celestijnenlaan 200D, B-3001 Leuven, Belgium\\
$^{12}$Department of Astrophysics, IMAPP, Radboud University Nijmegen, P.O. Box 9010, 6500 GL Nijmegen, The Netherlands\\
$^{13}$Kavli Institute for Theoretical Physics, University of California, Santa Barbara, CA 93106, USA\\
$^{14}$Institute for Astronomy, University of Hawai'i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA\\
$^{15}$SETI Institute, 189 Bernardo Avenue, Mountain View, CA 94043, USA\\
$^{16}$N\'{u}cleo de Astronom\'{i}a, Facultad de Ingenier\'{i}a y Ciencias, Universidad Diego Portales, Ej\'{e}rcito 441, Santiago De, Chile\\
}

@@

In addition, to the $\alpha$ and odd-Z elements we also derived the chemical abundance for several neutron capture elements including Sr, Zr, La, Eu (left panel of Fig~\ref{fig:ncap}) as well as Y, Ba, and Nd (right panel of Fig.~\ref{fig:ncap}).  It is clear from Fig.~\ref{fig:ncap}  that the chemical abundance ratio of neutron each neutron capture element is consistent with the Galactic disk population. We do however observe that the Ba of our sample is slightly enhanced while the Y of our sample is slightly compared to the general disk population of \cite{Bensby2014}. However, we conclude all elemental abundance ratios studied our sample most closely resemble the Galactic disk. 
\begin{figure*}
\noindent\includegraphics[width=0.7\textwidth,keepaspectratio]{chem_ncap_pope.pdf}

>>>>

% This author list is not final! If you think you should be in a different position please do not hesitate to say so.
\author[B. J. S. Pope et al.]{Benjamin J. S. Pope,$^{1,2,3}$\thanks{E-mail: benjamin.pope@nyu.edu}
Guy R. Davies,$^{4,5}$
Keith Hawkins,$^{6}$
Timothy R. White,$^{5,7}$\newauthor
Timothy R. Bedding,$^{8,5}$
Allyson Bieryla,$^{9}$
David W. Latham,$^{9}$,
Conny Aerts,$^{10,11,12}$\newauthor
Suzanne Aigrain,$^{3}$ 
Victoria Antoci,$^{5}$
Dominic M. Bowman,$^{10}$
Ashley Chontos,$^{8}$\newauthor
Gilbert A. Esquerdo,$^{9}$
Daniel Huber,$^{13,14,8}$
Paula Jofr\'{e},$^{15}$
Simon Murphy,$^{5,8}$\newauthor
Timothy van Reeth,$^{5,8}$
Victor Silva Aguirre,$^{5}$
Amalie Stokholm,$^{5}$
Jie Yu,$^{8,5}$ \newauthor
and friends
\\
% List of institutions
$^{1}$Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA\\
$^{2}$NASA Sagan Fellow\\
$^{3}$Oxford Astrophysics, Denys Wilkinson Building, University of Oxford, OX1 3RH, Oxford, UK\\
$^{4}$School of Physics and Astronomy, University of Birmingham, Birmingham B15 2TT, UK\\
$^{5}$Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, Ny Munkegade 120, DK-8000 Aarhus C, Denmark\\
$^{6}$Department of Astronomy, The University of Texas at Austin, 2515 Speedway Boulevard, Austin, TX 78712, USA\\
$^{7}$Research School of Astronomy and Astrophysics, Mount Stromlo Observatory, The Australian National University, Canberra, ACT 2611, Australia\\
$^{8}$Sydney Institute for Astronomy (SIfA), School of Physics, University of Sydney, NSW 2006, Australia\\
$^{9}$Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA\\
$^{10}$Institute of Astronomy, KU Leuven, Celestijnenlaan 200D, B-3001 Leuven, Belgium\\
$^{11}$Department of Astrophysics, IMAPP, Radboud University Nijmegen, P.O. Box 9010, 6500 GL Nijmegen, The Netherlands\\
$^{12}$Kavli Institute for Theoretical Physics, University of California, Santa Barbara, CA 93106, USA\\
$^{13}$Institute for Astronomy, University of Hawai'i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA\\
$^{14}$SETI Institute, 189 Bernardo Avenue, Mountain View, CA 94043, USA\\
$^{15}$N\'{u}cleo de Astronom\'{i}a, Facultad de Ingenier\'{i}a y Ciencias, Universidad Diego Portales, Ej\'{e}rcito 441, Santiago De, Chile\\
}

@@

In addition, to the $\alpha$ and odd-Z elements we also derived the chemical abundance for several neutron capture elements including Sr, Zr, La, Eu (left panel of Fig~\ref{fig:ncap}) as well as Y, Ba, and Nd (right panel of Fig.~\ref{fig:ncap}).  It is clear from Fig.~\ref{fig:ncap}  that the chemical abundance ratio of neutron each neutron capture element is consistent with the Galactic disk population. We do however observe that the Ba of our sample is slightly enhanced while the Y of our sample is slightly reduced relative to the general disk population of \cite{Bensby2014}. Nevertheless, we conclude all elemental abundance ratios studied our sample most closely resemble the Galactic disk. 
\begin{figure*}
\noindent\includegraphics[width=0.7\textwidth,keepaspectratio]{chem_ncap_pope.pdf}
